Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice

### 2017-05-30 reviewer_response.txt

Submission # 1137
Action Editor: Noah Smith

We would like to thank all of our reviewers for their detailed comments. We
have tried to address the important points as best we can, but were limited to
3 extra pages (beyond the 10 pages of the original submission). As all the
reviews had numerous suggestions for improvement, with only one obvious area
of overlap, we have had to pick and choose what we could add. In cases where
we did not change the paper, we provide a justification below.

We should mention one major change that wasn't prompted by individual reviewer
comments: there were clear misinterpretations by our original Japanese annotators
which led to overannotation of FS, leading us to do another round of annotation 
since the original submission. The Japanese results have therefore changed, and
are in fact more consistent with the other languages.

@@

> - After the equation for LPR, it would be good to give the intuition:
> choosing a context span such that w_i is more likely given its context words
> than its context POS tags.

This was removed from an earlier draft due to space, and we've added back in.

> - Inter-annotator agreement is surprisingly high. Could you elaborate on
> Wray’s criteria for FS that were applied by annotators?

Your surprise about the Kappa being high is based on a misunderstanding:
the kappa number reported in the table is after filtering to remove borderline
cases (i.e. it is the kappa for the final test set, not the original
sampling). To avoid confusion, we've added the original kappa score which is
quite a bit lower. Your intution is correct that there is significant
subjectivity to FS identification (more so than MWE annotation), and as such
we would never rely on a single annotator for building a FS test set. We have
not added more information about Wray's criteria; though it provide a starting
point for annotation, more relevant to achieving reasonable agreement are the
specific annotation guidelines which we created. Presenting them in the paper
would be too much of a digression, but we promise to make them public.

@@

> - I would like to see qualitative analysis of the sequences that were
> identified as formulaic (or not) by annotators/the method. E.g.: How many of
> them are syntactic constituents? Are there a wide variety of grammatical
> kinds of expressions? Are high-frequency as well as low-frequency sequences
> detected? What is the distribution in terms of length? What kinds of gapped
> sequences are there? It would be nice to see some examples.

In the discussion, we have added a thorough analysis of specific examples and
some statistics, including most of the information you ask for (implicitly if
not explicitly).

> - Related to the previous point: While noting the distinction between FS and
> MWEs, is it perhaps worth measuring recall against MWE datasets? Most MWEs
> apart from proper names should count as FS, right?

Do you mean as a way of evaluating different systems built on the same corpus,
or just to get a sense of coverage more generally? One central problem with
using recall for evaluation is that in order to make it fair, there must be
some control of the size of the lexicon. Neither our system nor our best
performing competitors are ranking models, none of them offer an easy or fair
way to simply take the best N words and look at recall. And even if they did,
there's other kinds of biases that would come into play: for instance, PMI and
similar metrics do well with rare terms that correspond well to the MWE
lexicon of WordNet, for instance, which (at the type level) is dominated by
certain kinds of terminology (biomedical terms, particularly) which are not
really used outside a very specific community. This relates to a more
fundamental problem with the idea of using recall in external lexicons as any
kind of useful measure: we could not expect any particular corpus (even a very
large one) to do justice to the full range of FS/MWE for a language, since
most of which appear regularly only within specific genres. For example, we
could not expect to build a good lexicon of English verb-particle
constructions from a biomedical corpus, because many are too informal to be
appropriate for that genre (e.g. "mess up"). With the qualitative analysis we
have added, the genre-specificity of the FS we extract is hopefully more clear.

### 2017-05-30 tacl.tex
Revised submission

\termdef{Soft covering} is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice. For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to occurrences of \ex{keep \gap under wraps}, with the idea that these occurrences have already been explained by the longer $n$-gram. If enough subsuming $n$-grams are on, then the shorter $n$-gram will be discounted to the extent that it will be turned off, preventing redundancy. This effect is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, and $a_1,\dotts, a_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes). Then, the $\cover(t)$ score for a covered node $t$ is:
\begin{displaymath}
\cover(t) = \max\Big(0,\frac{c(t) - \sum_{i=1}^{m}{c(a_i)}}{c(t)}\Big)
\end{displaymath}
This is intended as a simple, quick-to-calculate approximation of the result of recalculating minLPR with the counts corresponding to the covering nodes actually removed. The \cover score takes on values in the range 0 to 1, with 1 being the default when no covering occurs.

@@

In general, covering prefers turning on longer, covering $n$-grams since doing so explains nodes lower in the lattice. Not surprisingly, it is generally desirable to have a mechanism working in opposition, \ie one which views shorter FS as helping to explain the presence of longer $n$-grams which contain them, beyond the FS-neutral syntactic explanation provided by minLPR. \termdef{Clearing} does this by increasing the explainedness of nodes higher in the lattice when a lower node is turned-on. The basic mechanism is similar to covering, except that counts cannot be made use of in the same way---whereas it makes sense to explain covered nodes in proportion to the counts of their covering nodes (since the counts of the covered $n$-grams are from the covering $n$-gram), in the reverse direction this logic fails.

@@

Other than the inclusion of new languages, our test sets differ from \newcite{Brooke15b} in two ways. One advantage of a type-based annotation approach, particularly with regards to annotation with a known subjective component, is that it is quite sensible to simply discard borderline cases, improving reliability at the cost of some representativeness. To this end, we entirely excluded from our test set $n$-grams which just one annotator marked as FS. \tabref{tab:stats} contains the counts for the four test sets after this filtering step as well as Cohen's Kappa scores before (``Pre'') and after (``Post'').  The second change is that for the main evaluation we collapsed gapped and contiguous $n$-grams into a single test set. The rationale is that the number of positive gapped examples is too low to provide a reliable independent F-score.

@@

%The fact that less than 20\% of the FS derived from the BNC appear in the lexicon for the ICWSM corpus is fairly telling of how important genre differences are to the range of FS that will be seen in a particular corpus.
\tabref{tab:sample} contains 10 randomly selected examples from each of the lexicons produced by our method. Among the English examples, most of the clear errors are bigrams that reflect particular biases of their respective corpora: The phrase \ex{via slashdot} comes from boilerplate text identifying the source of a article, whereas \ex{Maureen} (from \ex{Maureen says}) is a character in one of the novels included in the BNC. The longer FS mostly seem sensible, in that they are plausible lexicalized constructions, though \ex{primarily as \gap and} from the BNC is not obviously an FS and likely the result of noise. Some FS are dialectal variants, for instance \ex{license endorsed} refers to the British traffic violations. More generally, the FS lexicons created by these two corpora are quite distinct, sharing less than 50\% of their entries.

@@

Since Zipfian frequency curves naturally extend to multiword vocabulary, our lexicons (and type-based evaluation of the them) are of course dominated by rarer terms. This is not, we would argue, a serious drawback, since in practical terms there is very little value in focusing on common FS like \ex{of course} which manually-built lexicons already contain; most of the potential in automatic extraction comes from the long tail. However, we did investigate the other end of the Zipfian curve by extracting the 20 most common MWEs (including both strong and weak) from the \newcite{Schneider14a} corpus. In the ICWSM lexicon, our recall for these common terms was fairly high (0.75), with errors mostly resulting from longer phrases containing these terms ``winning out'' (in the lattice) over shorter phrases, which have relatively low LPR due to extremely common constituent words; for example, we missed \ex{on time}, but had 19 FS which contain it (e.g.\ \ex{right on time}, \ex{show up on time}, and \ex{start on time}). 
%In one case which showed this same problem, \ex{waste * time}, the lexicon did have its ungapped version, highlighting potential for improvement.

@@

Though we have demonstrated that competition within a lattice is a powerful method for the production of FS lexicons, its usefulness derives less from the specific choices we have made in this instantiation of the model, and more from the flexiblity that such a model provides for future research. Not only do alternatives like DP-seg and LocalMaxs fail to scale up to large corpora, there are few obvious ways to improve on their simple underlying algorithms without compromising their elegance and worsening tractability. Fast and functional, the LPR decomp approach is nevertheless algorithmically ungainly, involving multiple layers of heuristic-driven filtering with no possibility of correcting errors. Our lattice method is aimed at something between these extremes: a practical, optimizable model, but with various component heuristics that can be improved upon. For instance, though the current version of clearing is effective and has practical advantages relative to simpler options that we tested, it could be enhanced by more careful investigation of the statistical properties of $n$-grams which contain FS.

>>>>

\termdef{Soft covering} is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice. For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to occurrences of \ex{keep \gap under wraps}, with the idea that these occurrences have already been explained by the longer $n$-gram. If enough subsuming $n$-grams are on, then the shorter $n$-gram will be discounted to the extent that it will be turned off, preventing redundancy. This effect is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, and $a_1,\dotts, a_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes). Then, the $\cover(t)$ score for a covered node $t$ is:
\begin{displaymath}
\cover(t) = \max\Big(0,\frac{c(t) - \sum_{i=1}^{m}{c(a_i)}}{c(t)}\Big)
\end{displaymath}
When applied as an exponent to a minLPR score, it serves as simple, quick-to-calculate approximation of a new minLPR with the counts corresponding to the covering nodes removed from the calculation. The \cover score takes on values in the range 0 to 1, with 1 being the default when no covering occurs.

@@

In general, covering prefers turning on longer, covering $n$-grams since doing so explains nodes lower in the lattice. Not surprisingly, it is generally desirable to have a mechanism working in opposition, \ie one which views shorter FS as helping to explain the presence of longer $n$-grams which contain them, beyond the FS-neutral syntactic explanation provided by minLPR. \termdef{Clearing} does this by increasing the explainedness of nodes higher in the lattice when a lower node is turned-on. The basic mechanism is similar to covering, except that counts cannot be made use of in the same way---whereas it makes sense to explain covered nodes in proportion to the counts of their covering nodes (since the counts of the covered $n$-grams can be directly attributed to the covering $n$-gram), in the reverse direction this logic fails.

@@

Other than the inclusion of new languages, our test sets differ from \newcite{Brooke15b} in two ways. One advantage of a type-based annotation approach, particularly with regards to annotation with a known subjective component, is that it is quite sensible to simply discard borderline cases, improving reliability at the cost of some representativeness. To this end, we entirely excluded from our test set $n$-grams which just one annotator marked as FS. \tabref{tab:stats} contains the counts for the four test sets after this filtering step as well as Fleiss' Kappa scores before (``Pre'') and after (``Post'').  The second change is that for the main evaluation we collapsed gapped and contiguous $n$-grams into a single test set. The rationale is that the number of positive gapped examples is too low to provide a reliable independent F-score.

@@

%The fact that less than 20\% of the FS derived from the BNC appear in the lexicon for the ICWSM corpus is fairly telling of how important genre differences are to the range of FS that will be seen in a particular corpus.
\tabref{tab:sample} contains 10 randomly selected examples from each of the lexicons produced by our method. Among the English examples, most of the clear errors are bigrams that reflect particular biases of their respective corpora: The phrase \ex{via slashdot} comes from boilerplate text identifying the source of a article, whereas \ex{Maureen} (from \ex{Maureen says}) is a character in one of the novels included in the BNC. The longer FS mostly seem sensible, in that they are plausible lexicalized constructions, though \ex{primarily as \gap and} from the BNC is not obviously an FS and likely the result of noise. Some FS are dialectal variants, for instance \ex{license endorsed} refers to British traffic violations. More generally, the FS lexicons created by these two corpora are quite distinct, sharing less than 50\% of their entries.

@@

Since Zipfian frequency curves naturally extend to multiword vocabulary, our lexicons (and type-based evaluation of the them) are of course dominated by rarer terms. This is not, we would argue, a serious drawback, since in practical terms there is very little value in focusing on common FS like \ex{of course} which manually-built lexicons already contain; most of the potential in automatic extraction comes from the long tail. However, we did investigate the other end of the Zipfian curve by extracting the 20 most common MWEs (including both strong and weak) from the \newcite{Schneider14a} corpus. In the ICWSM lexicon, our recall for these common terms was fairly high (0.75), with errors mostly resulting from longer phrases containing these terms ``winning out'' (in the lattice) over shorter phrases, which have relatively low LPR due to extremely common constituent words; for example, we missed \ex{on time}, but had 19 FS which contain it (e.g.\ \ex{right on time}, \ex{show up on time}, and \ex{start on time}). In one case which showed this same problem, \ex{waste * time}, the lexicon did have its ungapped version, highlighting the potential for improved handling of this issue.

@@

Though we have demonstrated that competition within a lattice is a powerful method for the production of multiword lexicons, its usefulness derives less from the specific choices we have made in this instantiation of the model, and more from the flexiblity that such a model provides for future research. Not only do alternatives like DP-seg and LocalMaxs fail to scale up to large corpora, there are few obvious ways to improve on their simple underlying algorithms without compromising their elegance and worsening tractability. Fast and functional, the LPR decomp approach is nevertheless algorithmically ungainly, involving multiple layers of heuristic-driven filtering with no possibility of correcting errors. Our lattice method is aimed at something between these extremes: a practical, optimizable model, but with various component heuristics that can be improved upon. For instance, though the current version of clearing is effective and has practical advantages relative to simpler options that we tested, it could be enhanced by more careful investigation of the statistical properties of $n$-grams which contain FS.
